Final Project

### 2020-11-18 chaloupka_sameshima_wallner_final_project.Rmd
Peer review
Added an image folder, and an inline image, plus a few ponderings.

---
title: "Final Project"
author: "Ben Chaloupka, Tess Sameshima, and Scott Wallner"
date: "10/26/2020"
output: pdf_document
---

>>>>

---
title: "Final Project"
author: "Ben Chaloupka, Tess Sameshima, and Scott Wallner"
date: "10/26/2020"
output: pdf_document
---
<!-- Using the papaja format would be good here, as it would provide a place for an abstract that would help the casual observer understand your project. -->

## "Our primary research question is whether observer dwell times systematically differ between growth and decay sequences when given the image of a fractal in growth or decay." 
![here is a serious sierpinski sequence](images/fractal_sequences.png)
